### 2019-10-01 proglog.tex
fixes tour info

\noindent{
\begin{minipage}{0.5\textwidth}
	\textbf{National Petascale Computing Facility (NPCF)}\\
Also located on campus is NCSA, which houses Blue Waters, one of the most powerful supercomputers in the world. The NCSA is within walking distance from all conference hotels. During the tour, attendees will tour the machine room and witness some of the beautiful results it produces. Supercomputers like Blue Waters are important for solving computationally challenging problems and creating robust simulations for a variety of phenomena.
\end{minipage}
\begin{minipage}{0.5\textwidth}
	\includegraphics[width=\textwidth]{bw_front.png}
	\captionof{figure}{Blue Waters Supercomputer}
\end{minipage}
}

@@

\noindent{\begin{minipage}{0.5\textwidth}
	\textbf{University Tour}\\
Attendees will be able to take a tour of the UIUC campus. They will start at the Talbot Laboratory where the department of Nuclear Plasma and Radiological Engineering is located. Here, students will get to see the Virtual Education and Research Laboratory to see how virtual reality technology can be adapted and applied to educational methods. There are also many other historical artifacts on display for participants to see. Afterwards, students will be led to various noteworthy locations unique to UIUC.
\end{minipage}
\begin{minipage}{0.5\textwidth}
	\centering
	\includegraphics[width=0.75\textwidth]{creek.png}
	\captionof{figure}{Engineering Hall on the Beautiful Engineering Quad}
\end{minipage}}
\\

>>>>

The tours of Blue Waters and Starfire Industries will be a combined tour. Visitors will spend approximately 1.5 hours at each location. These tours will depart from the hotel. 
\noindent{
\begin{minipage}{0.5\textwidth}
	\textbf{National Petascale Computing Facility (NPCF) - Blue Waters}\\
Also located on campus is NCSA, which houses Blue Waters, one of the most powerful supercomputers in the world. The NCSA is within walking distance from all conference hotels. During the tour, attendees will tour the machine room and witness some of the beautiful results it produces. Supercomputers like Blue Waters are important for solving computationally challenging problems and creating robust simulations for a variety of phenomena.
\end{minipage}
\begin{minipage}{0.5\textwidth}
	\includegraphics[width=\textwidth]{bw_front.png}
	\captionof{figure}{Blue Waters Supercomputer}
\end{minipage}
}

@@

\noindent{\begin{minipage}{0.5\textwidth}
	\textbf{NPRE Lab Tours}\\
Attendees will be able to take a tour of the various NPRE labs on campus. They will start at the Talbot Laboratory where the department of Nuclear Plasma and Radiological Engineering is located. Here, students will get to see the Virtual Education and Research Laboratory to see how virtual reality technology can be adapted and applied to educational methods. After, they will walk across the Engineering Quad to the Center for Plasma-Material Interactions (CPMI) where students conduct experiments on the stellerator-tokamak, HIDRA. There are also many other historical artifacts on display for participants to see. This tour will depart from the front entrance of the Illini Union.
\end{minipage}
\begin{minipage}{0.5\textwidth}
	\centering
	\includegraphics[width=0.75\textwidth]{creek.png}
	\captionof{figure}{Engineering Hall on the Beautiful Engineering Quad}
\end{minipage}}
\\
